Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from source FASTQ with STAR-HTSeq)

### 2016-09-20 code/Rmd/MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd
Minor modifications

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r covar_obj$properties$id`    |
|  Residual Expression      |  `r expr_obj$properties$id`     |
|  Differential Expression  |  `r dexp_obj$properties$id`     |

>>>>

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)

# Store logcpm values
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'logCPM.tsv', sep = '\t', row.names=F, quote=F)
exp1_obj = File('logCPM.tsv', name = 'Raw logCPM', parentId = CODE$properties$id)
exp1_obj = synStore(exp1_obj, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r covar_obj$properties$id`    |
|  Residual Expression      |  `r expr_obj$properties$id`     |
|  Differential Expression  |  `r dexp_obj$properties$id`     |
